---
title: "Dem_rep_bills_passed_115"
author: "arunakchutha"
date: "2022-12-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(tidyverse)
```

#####Load the data (if you want, you could do this locally from your computer rather than download from Dropbox)
```{r}
cel <- read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1"))

names(cel)
dim(cel)
table(cel$year)
summary(cel$all_bills)
```



#for making a scatterplot

####filter the data we want
```{r}
fig115 <- filter(cel,congress==115)
fig115 <- select(fig115,"seniority","all_pass")
```



####these commands do the same thing as above, just with piping
```{r}
fig115 <- cel %>% filter(congress==115) %>% select("seniority","all_pass")
```



###check to make sure the filter worked properly
```{r}

head(fig115)
```


####set up the data and aesthetics
```{r}
ggplot(fig115,aes(x=seniority,y=all_pass))
```



####add the marks
```{r}
ggplot(fig115,aes(x=seniority,y=all_pass))+
  geom_point()
```


####jitter adds random noise to the data to avoid overplotting
```{r}
ggplot(fig115,aes(x=seniority,y=all_pass))+
  geom_jitter()

```


####add some labels and a title
```{r}
ggplot(fig115,aes(x=seniority,y=all_pass))+
  geom_jitter()+
  labs(x="Seniority",y="Bills Passed",title="Seniority and Bills Passed in the 115th Congress")
```



#####modify filter and select to grab "dem"
```{r}
fig115 <- cel %>% 
  filter(congress==115) %>% 
  select("seniority","all_pass","dem")

fig115$dem

ggplot(fig115,aes(x=seniority,y=all_pass,color=dem))+
  geom_jitter()+
  labs(x="Seniority",y="Bills Passed",title="Seniority and Bills Passed in the 115th Congress")

```



####colors are strange, let's fix

#####make dem a categorical variable called "party"
```{r}
party <- recode(fig115$dem,`1`="Democrat",`0`="Republican")

fig115 <- add_column(fig115,party)

fig115$party

ggplot(fig115,aes(x=seniority,y=all_pass,color=party))+
  geom_jitter()+
  labs(x="Seniority",y="Bills Passed",title="Seniority and Bills Passed in the 115th Congress")
```



####let's make the colors match traditional blue democrats and red republicans
```{r}
ggplot(fig115,aes(x=seniority,y=all_pass,color=party))+
  geom_jitter()+
  labs(x="Seniority",y="Bills Passed",title="Seniority and Bills Passed in the 115th Congress")+
  scale_color_manual(values=c("blue","red"))
```




#####make two separate plots using facet_wrap
```{r}
ggplot(fig115,aes(x=seniority,y=all_pass,color=party))+
  geom_jitter()+
  labs(x="Seniority",y="Bills Passed",title="Seniority and Bills Passed in the 115th Congress")+
  scale_color_manual(values=c("blue","red"))+
  facet_wrap(~party)
```







